Template for indicator documentation

### 2023-12-05 insectIndicators.Rmd

```{r}
ggplot(richness_gdm_join) +
  geom_point(aes(x = no_species,
                 y = GDM,
                 color = region_name)) +
  geom_smooth(aes(x = no_species,
                 y = GDM,
                 color = region_name),
              method = lm) +
  scale_color_nina(name = "Region") +
  xlab("Antall arter")
```
<br/>
Interestingly, and perhaps reassuringly, the number of species doesn't seem to be clearly related to the average genetic diversity. We can look at the mean number of ASVs as well.

```{r}
ggplot(richness_gdm_join) +
  geom_point(aes(x = mean_no_asv_per_species,
                 y = GDM,
                 color = region_name)) +
  geom_smooth(aes(x = mean_no_asv_per_species,
                 y = GDM,
                 color = region_name),
              method = lm) +
  scale_color_nina(name = "Region") +
  xlab("Antall genetiske varianter per art")
```
<br/>
Here we see a positive relationship in Trøndelag (although uncertain), but not the other regions.

```{r}
ggplot(richness_gdm_join) +
  geom_point(aes(x = no_species,
                 y = mean_no_asv_per_species,
                 color = region_name)) +
  geom_smooth(aes(x = no_species,
                 y = mean_no_asv_per_species,
                 color = region_name),
              method = lm) +
  scale_color_nina(name = "Region") +
  xlab("Antall arter") +
  ylab("Antall genetiske varianter per art")

@@

```{r echo = T, results = "hide"}

>>>>

```{r}
ggplot(richness_gdm_join) +
  geom_point(aes(x = no_species,
                 y = GDM,
                 color = region_name)) +
  geom_smooth(aes(x = no_species,
                 y = GDM,
                 color = region_name),
              method = lm) +
  NinaR::scale_color_nina(name = "Region") +
  xlab("Antall arter")
```
<br/>
Interestingly, and perhaps reassuringly, the number of species doesn't seem to be clearly related to the average genetic diversity. We can look at the mean number of ASVs as well.

```{r}
ggplot(richness_gdm_join) +
  geom_point(aes(x = mean_no_asv_per_species,
                 y = GDM,
                 color = region_name)) +
  geom_smooth(aes(x = mean_no_asv_per_species,
                 y = GDM,
                 color = region_name),
              method = lm) +
  NinaR::scale_color_nina(name = "Region") +
  xlab("Antall genetiske varianter per art")
```
<br/>
Here we see a positive relationship in Trøndelag (although uncertain), but not the other regions.

```{r}
ggplot(richness_gdm_join) +
  geom_point(aes(x = no_species,
                 y = mean_no_asv_per_species,
                 color = region_name)) +
  geom_smooth(aes(x = no_species,
                 y = mean_no_asv_per_species,
                 color = region_name),
              method = lm) +
  NinaR::scale_color_nina(name = "Region") +
  xlab("Antall arter") +
  ylab("Antall genetiske varianter per art")

@@

```{r echo = T, results = "hide", eval = FALSE}
